# Report 4
## Exercises
### Part 1
#### Get the full dataset out of the site. Your code should end up with a tibble of a bit more than 600 rows and 9 columns. Make sure you take the time to convert each columns to the right type and not all character

```{r}
library(xml2)
library(rvest)
library(textclean)
library(lubridate)
library(concatenate)
library(stringr)
library(dplyr)

page_html <- xml2::read_html("https://epfl-exts.github.io/rental-scrape/")

numextract <- function(string){ 
  str_extract(string, "\\-*\\d+\\.*\\d*")
} 

object_type <- page_html %>%
  rvest::html_nodes(css = ".object-type") %>%
  rvest::html_text()

rooms <- page_html %>%
  rvest::html_nodes(css = ".rooms strong") %>%
  rvest::html_text() 

price <- page_html %>%
  rvest::html_nodes(css = ".float-right strong") %>%
  rvest::html_text() 

address <- page_html %>%
  rvest::html_nodes(css = ".address p") %>%
  rvest::html_text() 

living_space <- page_html %>%
  rvest::html_nodes(css = ".living-space strong") %>%
  rvest::html_text() %>%
  numextract 

floor <- page_html %>%
  rvest::html_nodes(css = ".floor strong") %>%
  rvest::html_text() 

usable_surface <- page_html %>%
  rvest::html_nodes(css = ".usable-surface strong") %>%
  rvest::html_text() %>%
  numextract

availability <- page_html %>%
  rvest::html_nodes(css = ".availability strong") %>%
  rvest::html_text() 

rentals <-
  as_tibble(cbind(object_type, rooms, price, address, living_space, floor, usable_surface, availability)) %>%
  mutate(rooms = as.integer(rooms),
         price = as.integer(price),
         living_space = as.integer(living_space),
         floor = as.integer(floor),
         usable_surface = as.integer(usable_surface),
         availability = dmy(availability),
         postcode = as.integer(str_extract(address, "\\d{4}")))

```

### Part 2
#### Create a scatterplot showing how price evolves with living space of the flat.

```{r}
library(ggplot2)
rentals_scatterplot <-
  rentals %>%
  filter(!is.na(price) & !is.na(living_space))

ggplot(rentals_scatterplot, aes(x=living_space, y=price)) + 
  geom_point(alpha=0.5) +
  labs(title="How the price evolves with living space",
       x="living space in m2", y="price in CHF") 

```

### Part 3
#### Create a bar plot showing the number of properties by postcode. Is this agency more "active" in certain areas?

```{r}
library(ggplot2)

by_postcode <-
rentals %>%
  group_by(postcode) %>%
  summarise(sum = n()) %>%
  arrange(desc(sum))

ggplot(data=by_postcode, 
       mapping=aes(x=postcode, y=sum)) + 
  geom_bar(stat="identity") + 
  labs(title="Number of rentals by postcode",
       x="rentals", y="postcode") 


```

Yes. They are more active in certain areas.

### Part 4
#### Create a more complex scatterplot, showing how price evolves with living space of the flat by postcode and by floor. You can use colors and/or facets to make the categories visible.

```{r}
rentals_scatterplot <-
  rentals %>%
  filter(!is.na(price) & !is.na(living_space) & floor > 0 & floor < 7)


ggplot(rentals_scatterplot, aes(x=living_space, y=price, color=postcode)) + 
  geom_point(alpha=0.5, size=3) +
  labs(title="How the price evolves with living space",
       x="living space in m2", y="price in CHF") +
  facet_wrap(~floor) +
  theme(legend.position = "none")

```

### Part 5
#### Can you see any trends for listings with addresses only available on demand? Are they more expensive or less? Bigger living space? Higher floor? Keep in mind that boxplot/violin plots work really well to compare distributions of values between groups!
```{r}

rentals %>%
  filter(str_detect(address, "Address on request") |   str_detect(address, "sur demande"))


```
