```{r include=FALSE}
library(dplyr)


professors <- read.csv("~/Documents/data_course/projects/professors.csv")
students <- read.csv("~/Documents/data_course/projects/students.csv")

```

# Report 1
## Exercises
### Part 1
#### What is the total number of answers obtained from students?
```{r}
student_answers_per_question <-
students %>%
group_by(X) %>%
mutate(answers = sum(Totally.Disagree, Totally.agree, Agree, Disagree))
total_answers_students <- sum(student_answers_per_question["answers"])
```
`r total_answers_students` is the total number of answers obtained from students.

#### What is the total number of answers obtained from professors?
```{r}
professor_answers_per_question <-
professors %>%
group_by(X) %>%
mutate(answers = sum(Totally.Disagree, Totally.agree, Agree, Disagree))
total_answers_professors <- sum(professor_answers_per_question["answers"])

```
`r total_answers_professors` is the total number of answers obtained from professors.

#### Does each question have the same number of answers?
```{r}

deviation_students <- 
student_answers_per_question %>%
  ungroup %>%
  pull(answers) %>%
  sd 

deviation_professors <- 
professor_answers_per_question %>%
  ungroup %>%
  pull(answers) %>%
  sd
```
As the deviation is not equal 0 (it is `r round(deviation_students, 3)` for students/`r round(deviation_professors, 3)` for professors) therefore not all questions have the same number of answers.

\newpage
### Part 2
#### Obtain side-by-side bar charts comparing the distribution of answers of the students versus the professors for each question.
```{r}
library(ggplot2)


```

