```{r include=FALSE}
library(dplyr)
library(tidyr)
library(DBI)
library(purrr)

politicians_db <- dbConnect(RSQLite::SQLite(), "zh_politicians.db")

addresses_tbl <- tbl(politicians_db, "Addresses")
affilations_tbl <- tbl(politicians_db, "Affiliations")
mandates_tbl <- tbl(politicians_db, "Mandates")
persons_tbl <- tbl(politicians_db, "Persons")

library(lubridate)
library(janitor)

mandates <-
mandates_tbl %>%
  collect

persons <- 
persons_tbl %>%
  collect 

affilations <-
affilations_tbl %>%
  collect

addresses <- 
addresses_tbl %>%
  collect

```

# Report 3
## Exercises
### Part 1
#### How many survey participants were there?
```{r}

mandates <-
mandates %>%
  filter(MANDATE_START_DAY > 0) %>%
  mutate(StartDate = make_date(MANDATE_START_YEAR, MANDATE_START_MONTH, MANDATE_START_DAY),
         MANDATE_END_YEAR = case_when(
         MANDATE_END_YEAR==0 ~ as.integer(format(Sys.Date(),'%Y')),
         TRUE ~ MANDATE_END_YEAR),
         MANDATE_END_MONTH = case_when(
         MANDATE_END_MONTH==0 ~ as.integer(format(Sys.Date(),'%m')),
         TRUE ~ MANDATE_END_MONTH),
         MANDATE_END_DAY = case_when(
         MANDATE_END_DAY==0 ~ as.integer(format(Sys.Date(),'%d')),
         TRUE ~ MANDATE_END_DAY),
         EndDate = make_date(MANDATE_END_YEAR, MANDATE_END_MONTH, MANDATE_END_DAY),
         active_years = map2(MANDATE_START_YEAR, MANDATE_END_YEAR, seq)) 
  
unnested_data <-
unnest(mandates, active_years) %>%
  group_by(active_years, ASSEMBLY) %>%
  summarise(sum = n())


library(ggplot2)
ggplot(data=unnested_data, 
       mapping=aes(x=active_years, y=sum, color=ASSEMBLY)) + 
  geom_line() + 
  labs(title="Number of active mandats per year",
       subtitle="The peaks are caused by election years when multiple mandates were active for the same seat",
       x="years", y="n") 
```


### Part 2
#### Expand on the plot you just produced. This time you want to show a facet charts with one chart per assembly. In each chart, have one line for men and one line for women.

```{r}

mandates_with_names <- left_join(mandates, persons, by = c("PERSON_ID" = "ID"))

unnested_data <-
unnest(mandates_with_names, active_years) %>%
  group_by(active_years, ASSEMBLY, GENDER) %>%
  filter(GENDER != "") %>%
  summarise(sum = n())

ggplot(data = unnested_data, 
       mapping=aes(x=active_years, y=sum, color=GENDER)) + 
  geom_line() + 
  labs(title="Number of active mandats per year by assembly",
       x="years", y="n") +
  facet_wrap(~ASSEMBLY)

```


### Part 3
#### Create a new plot showing the proportion of elected politicians from each party in year 2000. You want to show this by assembly, so use one facet with one pie chart per assembly.

```{r}

politicians_in_2000 <-
unnest(mandates, active_years) %>%
  filter(active_years == 2000) %>%
  left_join(affilations, by = c("ID" = "MANDATE_ID")) %>%
  select(PARTY, ASSEMBLY) %>%
  group_by(PARTY, ASSEMBLY) %>%
  summarise(sum = n())


```

### Part 4
#### Have another look at the composition of the assemblies: this time use a line chart to show how it changed over the years. (parlement composition for each year with the number of representative by affiliation)

```{r}

part4 <-
affilations %>%
  filter(PERSON_ID > 0 & AFFILIATION_START_YEAR > 0 & AFFILIATION_END_YEAR < 2021) %>%
    mutate(AFFILIATION_END_YEAR = case_when(
         AFFILIATION_END_YEAR==0 ~ as.integer(format(Sys.Date(),'%Y')),
         TRUE ~ AFFILIATION_END_YEAR),
         active_years = map2(AFFILIATION_START_YEAR, AFFILIATION_END_YEAR, seq)) %>%
    left_join(mandates, by = c("MANDATE_ID" = "ID"))

unnested_data <-
unnest(part4, active_years.x) %>%
  group_by(active_years.x, ASSEMBLY) %>%
  summarise(sum = n())

ggplot(unnested_data, aes(x=active_years.x, y=sum, color=ASSEMBLY)) +
  geom_line(aes(linetype=ASSEMBLY))+
  facet_wrap(~ASSEMBLY)+ 
  theme(legend.position = "none")

```

### Part 5
#### For the politicians that have a YEAR_OF_DEATH in the data, find the average life span. Does it change if you go by a TITLE? Use a plot to show the difference (or its absence).


```{r}

persons_age <-
persons %>%
  mutate(YEAR_OF_BIRTH = as.integer(YEAR_OF_BIRTH),
         YEAR_OF_DEATH = as.integer(YEAR_OF_DEATH)) %>%
  filter(YEAR_OF_BIRTH > 0 & !is.na(YEAR_OF_DEATH)) %>%
  mutate(life_span = YEAR_OF_DEATH - YEAR_OF_BIRTH)  %>%
  filter(life_span > 20 & life_span < 120)

avg_overall <-
persons_age %>%
  summarise(avg_life_span = round(mean(life_span),1))

avg_by_title <-
persons_age %>%
  group_by(TITLE) %>%
  summarise(avg_life_span = mean(life_span)) %>%
  arrange(avg_life_span) 
  
avg_overall
avg_by_title

```

### Part 6
#### Which politicians have had the most mandates? Create a top 10 horizontal bar chart.


```{r}

library(stringr)

max_mandates <-
mandates %>%
  group_by(PERSON_ID) %>%
  summarise(sum = n()) %>%
  arrange(desc(sum)) %>%
  top_n(10) %>%
  left_join(persons, by = c("PERSON_ID" = "ID")) %>%
  select(FIRSTNAME, LASTNAME, sum) %>%
  mutate(name = stringr::str_glue("{FIRSTNAME} {LASTNAME}"))

ggplot(data= max_mandates, 
       mapping=aes(x=name, 
                   y=sum)) + 
  geom_bar(stat="identity", position = "dodge") + 
  coord_flip() +
  labs(title="Politicians with most mandates",
       x="sum of mandates")

```

### Part 7
#### Do some politicians have multiple mandates at the same time?


```{r}



  

```

### Part 8
#### Have some politicians been affiliated to different parties over the years?

```{r}

politicians_more_than_one_party <-
affilations %>%
  group_by(PERSON_ID, PARTY) %>%
  summarise(sum = n()) %>%
  arrange(desc(sum)) %>%
  filter(sum > 1) %>%
  nrow()
politicians_more_than_one_party
```
`r politicians_more_than_one_party` politicians have been affiliated to more than one party

### Part 9
#### Take a sample of 20 politicians with a listed address and plot them on a {leaflet} map. You will need to use an API that converts the addresses to geocoordinates.

```{r}
library(leaflet)
library(httr)
library(purrr)
library(leaflet)



addresses_part9 <-
addresses %>%
  filter(!is.na(STREET) & HOUSE_NUMBER > 0 & POSTAL_CODE > 0) %>%
  mutate(POSTAL_CODE = str_extract(POSTAL_CODE, "\\d{4}"),
    address = str_glue("{STREET}+{HOUSE_NUMBER}+{POSTAL_CODE}+{CITY}")) %>%
  head(20) 



geolocations <-
str_glue("https://geocode.xyz/{addresses_part9$address}?json=1") %>%
  map(httr::GET) %>%
  map(content, as = "parsed") 

longt <- map(geolocations, pluck, "longt")
latt <- map(geolocations, pluck, "latt")

cords <-
  as_tibble(cbind(longt, latt)) %>%
  mutate(longt = as.double(longt),
         latt = as.double(latt)) 

cords %>%
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng=~longt,lat=~latt)
         
  
```

{r include=FALSE}
dbDisconnect(politicians_db)
```
