```{r include=FALSE}
library(dplyr)


professors <- read.csv("~/Documents/data_course/projects/professors.csv")
students <- read.csv("~/Documents/data_course/projects/students.csv")

```

# Report 1
## Exercises
### Part 1
#### What is the total number of answers obtained from students?
```{r}
student_answers_per_question <-
students %>%
group_by(X) %>%
mutate(answers = sum(Totally.Disagree, Totally.agree, Agree, Disagree))
total_answers_students <- sum(student_answers_per_question["answers"])
```
`r total_answers_students` is the total number of answers obtained from students.

#### What is the total number of answers obtained from professors?
```{r}
professor_answers_per_question <-
professors %>%
group_by(X) %>%
mutate(answers = sum(Totally.Disagree, Totally.agree, Agree, Disagree))
total_answers_professors <- sum(professor_answers_per_question["answers"])

```
`r total_answers_professors` is the total number of answers obtained from professors.

#### Does each question have the same number of answers?
```{r}

deviation_students <- 
student_answers_per_question %>%
  ungroup %>%
  pull(answers) %>%
  sd 

deviation_professors <- 
professor_answers_per_question %>%
  ungroup %>%
  pull(answers) %>%
  sd
```
As the deviation is not equal 0 (it is `r round(deviation_students, 3)` for students/`r round(deviation_professors, 3)` for professors) therefore not all questions have the same number of answers.

\newpage
### Part 2
#### Obtain side-by-side bar charts comparing the distribution of answers of the students versus the professors for each question.
```{r}

library(ggplot2)
library(tidyr)

to_visualize <-
students %>%
  gather(
    key = "type_of_response",
    value = "answers",
    Totally.agree, Agree, Disagree, Totally.Disagree)

students_visualize <- mutate(to_visualize, who = "students") 

to_visualize <-
professors %>%
  gather(
    key = "type_of_response",
    value = "answers",
    Totally.agree, Agree, Disagree, Totally.Disagree)

professors_visualize <- mutate(to_visualize, who = "professors") 

bound_data <-bind_rows(students_visualize, professors_visualize)

  ggplot(data= bound_data, 
       mapping=aes(x=type_of_response, 
                   y=answers,
                   fill=who)) + 
  geom_bar(stat="identity", position = "dodge", ) + 
  scale_x_discrete(labels = c("Totally.agree", "Agree", "Disagree", "Totally.disagree")) +
  labs(title="My side-by-side facet chart",
       subtitle="Using facet to show each questions",
       x="type of response", y="count of response") +
  facet_wrap(~X) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

```

\newpage
### Part 3
#### The most appropriate measure of central tendency is the mode. Compute the mode for the students and professors for each of the questions.
```{r}

Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

students_mode <-
students %>%
  group_by(X) %>%
  mutate(mode=Mode(c(Totally.agree, Agree, Disagree, Totally.Disagree)))

students_mode

professors_mode <-
professors %>%
  group_by(X) %>%
  mutate(mode=Mode(c(Totally.agree, Agree, Disagree, Totally.Disagree)))

professors_mode

```
