```{r include=FALSE}
library(readxl)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)


athletes <- read_excel("olympics.xlsx", sheet = "athletes")
country <- read_excel("olympics.xlsx", sheet = "country")
games <- read_excel("olympics.xlsx", sheet = "games")
medals <- read_excel("olympics.xlsx", sheet = "medals")
```

# Report 6
## Exercises
### Part 1
#### Have some athletes competed for different countries over time?

```{r}
summary_athletes <-
country %>%
  group_by(athlete_id) %>%
  mutate(n = n(),
         differnet_countries = n_distinct(NOC)) %>%
  arrange(desc(differnet_countries)) 
summary_athletes

left_join(summary_athletes, athletes, by = c("athlete_id" = "ID")) 
```
There are several athletes who have competed for different countries.


### Part 2
#### Who are the ten athletes that took part in most games?
```{r}

max_participations <-
country %>%
  group_by(athlete_id) %>%
  summarise(participations = n()) %>%
  top_n(10) %>%
  arrange(desc(participations))
max_participations
left_join(max_participations, athletes, by = c("athlete_id" = "ID")) %>%
  select(Name, participations)

```

### Part 3
#### What athlete(s) kept a Gold medal for the longest time?
```{r}

analysis <-
medals %>%
  filter(Medal == "Gold") %>%
  mutate(year = as.integer(str_extract(Games, "\\d{4}"))) %>%
  distinct(athlete_id, Event, year) %>%
  group_by(athlete_id, Event) %>%
  arrange(year) %>%
  mutate(lag = lag(year, 1),
         diff = year-lag,
         sum = n(),
         calc1 = case_when((year - lag) != 4 ~ 1, 
                             TRUE ~ 0),
         cumsumcalc = cumsum(calc1),
         count = n_distinct(cumsumcalc)) %>%
  ungroup() %>%
  arrange(desc(count)) 


analysis
```

### Part 4
#### What country(ies) kept a Gold medal for the longest time?

```{r}
analysis <-
medals %>%
  filter(Medal == "Gold") %>%
  mutate(year = as.integer(str_extract(Games, "\\d{4}"))) %>%
  distinct(Team, Event, year) %>%
  group_by(Team, Event) %>%
  arrange(year) %>%
  mutate(lag = lag(year, 1),
         diff = year-lag,
         sum = n(),
         calc1 = case_when((year - lag) != 4 ~ 1, 
                             TRUE ~ 0),
         cumsumcalc = cumsum(calc1),
         count = n_distinct(cumsumcalc)) %>%
  arrange(desc(count))

analysis
```

### Part 5
#### Who are the ten athletes that competed in the most events (some athletes take part in more than one event during games) ?

```{r}
analysis <-
medals %>%
  group_by(athlete_id) %>%
  summarise(different_events = n_distinct(Event)) %>%
  arrange(desc(different_events)) %>%
  top_n(10) %>%
  left_join(athletes, by = c("athlete_id" = "ID")) %>%
  select(Name, different_events)
analysis
```

### Part 6
#### Create a new table showing the number of medals per country (rows) and per year (column). Keep only the 15 countries with the most medals overall.

```{r}

analysis <-
medals %>%
  filter(Medal == "Gold" | Medal == "Silver" | Medal == "Bronze") %>%
  distinct(Team, Event, Games) %>%
  mutate(year = as.integer(str_extract(Games, "\\d{4}"))) %>%
  group_by(Team, year) %>%
  summarise(sum = n()) %>%
  group_by(Team) %>%
  mutate(medals_overall = sum(sum)) %>%
  tidyr::spread(key = "year",
                value = "sum") %>%
  arrange(desc(medals_overall)) %>%
  top_n(15)

analysis
```

### Part 7
#### Create a scatterplot showing the average height and weight of competitors per sport (one dot per sport). Add labels with the sport names for:
* the largest average height
* the largest average weight
* the smallest average height
* the smallest average weight
* the largest average BMI
* the smallest average BMI

```{r}
part_7 <-
medals %>%
  left_join(athletes, by = c("athlete_id" = "ID")) %>%
  filter(!is.na(Height) & !is.na(Weight)) %>%
  mutate(bmi=Weight / ((Height/100)*(Height/100))) %>%
  group_by(Sport) %>%
  summarise(avg_height = mean(Height),
            avg_weight = mean(Weight),
            avg_bmi = mean(bmi)
            )

labels = summarise(part_7,
                   max_avg_height = max((avg_height)),
                   min_avg_height = min((avg_height)),
                   max_avg_weight = max((avg_weight)),
                   min_avg_weight = min((avg_weight)),
                   max_avg_bmi = max((avg_bmi)),
                   min_avg_bmi = min((avg_bmi)))

part_7

ggplot(part_7, aes(x=avg_height, y=avg_weight)) + 
  geom_point(alpha=0.7)  +
  geom_text(aes(label=ifelse(avg_height>=labels$max_avg_height,as.character(Sport),'')),hjust=0.55,vjust=1.5) +
  geom_text(aes(label=ifelse(avg_weight>=labels$max_avg_weight,as.character(Sport),'')),hjust=0.55,vjust=1.5) +
  geom_text(aes(label=ifelse(avg_bmi>=labels$max_avg_bmi,as.character(Sport),'')),hjust=0.55,vjust=1.5) +
  geom_text(aes(label=ifelse(avg_height<=labels$min_avg_height,as.character(Sport),'')),hjust=0.4,vjust=1.5) +
  geom_text(aes(label=ifelse(avg_weight<=labels$min_avg_weight,as.character(Sport),'')),hjust=0.55,vjust=1.5) +
  geom_text(aes(label=ifelse(avg_bmi<=labels$min_avg_bmi,as.character(Sport),'')),hjust=0.55,vjust=1.5) 
  
```



### Part 8
#### Create a line plot showing the number of medals given by year (one line for Gold, one line for Silver and one line for Bronze). Does it change over time? Use facet to separate the medals at Summer games and Winter games.

```{r}

part_8 <-
medals %>%
  filter(Medal == "Gold" | Medal == "Silver" | Medal == "Bronze") %>%
  group_by(Games, Medal) %>%
  summarise(amount_of_medals = n()) %>%
  mutate(year = as.integer(str_extract(Games, "\\d{4}")),
         type = ifelse(str_detect(Games, "Summer"), "Summer games", "Winter games"))

ggplot(part_8, aes(x=year, y=amount_of_medals, color=Medal)) + 
  geom_line() +
  labs(title="Medals per year",
       x="year", y="medals") +
  facet_wrap(~type) 

```

The amount of medal increases over time. Only after the first and after the second world war there was a decline in amount for the summer olympics.

