```{r include=FALSE}
library(dplyr)


survey_data <- read.csv("~/Documents/data_course/projects/survey.csv")

```

# Report 2
## Exercises
### Part 1
#### How many survey participants were there?
```{r}
#number_of_participants <-
survey_data <-
survey_data %>%
  mutate(Sum.participants = Number.of.employees+Number.of.PhD.students+Number.of.postdocs+Number.of.professors)
  
number_of_participants <-
  survey_data %>%
  summarize(sum = sum(Sum.participants))
```
There were `r toString(number_of_participants)` participants.

#### What are the data types of each column?
```{r}
sapply(survey_data, class)
```
All numbers (X, Number of employees, number of PhD students, nunber of postdocs, number of professors are integer.

University, position and sizes are factor.

#### What are the top 3 universities with the most survey participants?
```{r}
top_3_by_participants <-
survey_data %>%
  arrange(desc(Sum.participants)) %>%
  slice(1:3) %>%
  select(University, Sum.participants)
top_3_by_participants
```
University of Groningen, Leiden University and Delft University of Technology are the top 3 universities with the most survey participants.

### Part 2
#### Obtain a horizontal bar graph of the number of survey participants for the different positions given in the column Position
```{r}
library(ggplot2)

no_of_servey_participants_by_position <- 
survey_data %>%
  group_by(Position) %>%
  summarise(sum = sum(Number.of.employees)) %>%
  arrange(desc(sum))

ggplot(data=no_of_servey_participants_by_position, 
       mapping=aes(y=sum, x=Position)) + 
  geom_bar(stat="identity") + 
  labs(title="Number of survey participants for the different positions",
       x="Position", y="Number of survey participants") +
  coord_flip()
```

### Part 3
There is a column (named Sizes) in the dataset that is supposed to group the data in the column Number of employees in the following bins:

Small (0 to 10)
Medium (11 to 20)
Large (21 to 100)
Extra large (over 100)
Unfortunately, somebody made mistakes in that column…

Recreate this column correctly, then plot a bar chart with {ggplot2} of the number of values in each of the bins.
```{r}
corrected_data <-
survey_data %>%
  mutate(Sizes= case_when(
    Number.of.employees <= 10 ~ "Small (0 to 10)",
    Number.of.employees <= 20 ~ "Medium (11 to 20)",
    Number.of.employees <= 100 ~ "Large (21 to 100)",
    TRUE ~ "Extra large (over 100)"
  ))

distribution_of_sizes <-
corrected_data %>%
  group_by(Sizes) %>% 
  tally()

ggplot(data=distribution_of_sizes, 
       mapping=aes(y=n, x=Sizes)) + 
  geom_bar(stat="identity") + 
  labs(title="Number of values in each of the bins",
       x="Sizes", y="Number of employees") +
  coord_flip()
```

### Part 4
Obtain a stacked horizontal bar plot with {ggplot2} that gives the percentage of employees that are Ph.D. students, postdocs and professors for each research group. 

```{r}
library(tidyr)

#GATHER 
percentages <-
corrected_data %>%
  mutate(Percentage.students=100/Number.of.employees*Number.of.PhD.students,
    Percentage.postdocs=100/Number.of.employees*Number.of.postdocs,
    Percentage.professors=100/Number.of.employees*Number.of.professors) %>%
  tidyr::gather(
    key = "percentage_type",
    value = "percentage",
    Percentage.students, Percentage.postdocs, Percentage.professors)


ggplot(data = percentages, aes(x = X, y = percentage, fill = factor(percentage_type)))+
  geom_bar(stat="identity") +
  coord_flip() +
  labs(title="Employees role percentages for each group",
       subtitle="We can see that groups can have very different splits",
       x="Research group ID", y="Percentage") +
  theme(legend.position="bottom")+
  guides(fill=guide_legend(title="Employee type"))+
  scale_x_continuous(breaks = seq(1, 30, by = 1))
  


```
