```{r include=FALSE}
library(dplyr)


professors <- read.csv("~/Documents/data_course/projects/professors.csv")
students <- read.csv("~/Documents/data_course/projects/students.csv")

```

# Report 1
## Exercises
### Part 1
#### What is the total number of answers obtained from students?
```{r}
student_grouped_by_question <- group_by(students, X)
  student_answers_per_question <- mutate(student_grouped_by_question, answers = sum(Totally.Disagree, Totally.agree, Agree, Disagree))
  total_answers_students <- sum(student_answers_per_question["answers"])
```
`r total_answers_students`

#### What is the total number of answers obtained from professors?
```{r}
professor_grouped_by_question <- group_by(professors, X)
  professor_answers_per_question <- mutate(professor_grouped_by_question, answers = sum(Totally.Disagree, Totally.agree, Agree, Disagree))
  total_answers_professor <- sum(professor_answers_per_question["answers"])
```
`r total_answers_professor`

#### Does each question have the same number of answers?
```{r}

```

\newpage
### Part 2
#### Obtain side-by-side bar charts comparing the distribution of answers of the students versus the professors for each question.
```{r}
library(ggplot2)


```

